---
title: "120 Years of Olympic Games"
author: "Yafeng (Jason) Zhou, Lan (Claudia) Lou, Yushi Pu, Zeyu (Jeremy) Zhang"
date: "12/3/2019"
output:
  pdf_document: default
  beamer_presentation: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
#install.packages("ggplot2")
#install.packages("tidyverse")
#install.packages("gridExtra")
#install.packages("plotly")
library(plotly)
library(gridExtra)
library(knitr)
library(dplyr)
library(ggplot2)
library(magrittr)
library(ggmap)
library(stringr)
#five functions in tidyverse: 
  #filter(), 
  #select(), 
  #mutate(),
  #arrange(), and 
  #group_by() / summarize()
#combining these to do gender
#ctl + shift +m for %>% 

#reading the data
athletes <- read.csv("D:/athlete_events.csv")
regions <- read.csv("D:/noc_regions.csv")
```

## The Dataset

Modern Olympic Games have a long history that can be tracaed back to more than a century ago. This dataset consists of information about Olympic Games athletes over the past 120 years, including...

- Name
- Age
- Weight
- Height
- Country of origin
- Sports

And information on the Olympic Games they participated in, such as...

- Year of the Olympic
- City in which the Game is held
- Season (Summer/Winter)

Now, let us take you through the 120 years of Olympic history. 
We will explore how the Olympic Games empitomizes **social trends** and uncover some **interesting topics**...

****
## How is Participation Rates Change Over Time?
```{r}
athletes %>%
  #reflect Year to winter&summer olympic games
  group_by(Year, Season) %>%
  #get number of participants of each time of olympic games
  summarise(NumberOfParticipants = n()) %>%
  ggplot(aes(x = Year, y = NumberOfParticipants, group = Season)) +
  geom_line(aes(color = Season)) +
  geom_point(aes(color = Season)) +
  annotate("text", x=c(1936,1956,1976,1980,2016),
           y=c(3000,4500,8000,6000,14000),
           label=c("Berlin 1936","Melbourne 1956","Montreal 1976","Moscow 1980","Rio 2016"),
           size=2) +
  labs(x = "Year", y = "Count", title = "Number of Participants in the Olympic Games")+ theme(plot.title = element_text(hjust = 0.5))
```

****
## How is Participating Rates affected by Historical Events?
### ggmap()

### At the early stage of the Olympic Games, most of the participating countries came from Europe
```{r}
# Add regions to data and remove missing points
data_regions <- athletes %>% 
  left_join(regions,by="NOC") %>%
  filter(!is.na(region))

# Subset to Games of interest and count athletes from each country

Stockholm <- data_regions %>% 
  filter(Games == "1912 Summer") %>%
  group_by(region) %>%
  summarize(Stockholm = length(unique(ID)))

Berlin <- data_regions %>% 
  filter(Games == "1936 Summer") %>%
  group_by(region) %>%
  summarize(Berlin = length(unique(ID)))

Tokyo <- data_regions %>% 
  filter(Games == "1964 Summer") %>%
  group_by(region) %>%
  summarize(Tokyo = length(unique(ID)))

Montreal <- data_regions %>% 
  filter(Games == "1976 Summer") %>%
  group_by(region) %>%
  summarize(Montreal = length(unique(ID)))

Moscow <- data_regions %>%
  filter(Games == "1980 Summer") %>%
  group_by(region) %>%
  summarise(Moscow = length(unique(ID)))

rio <- data_regions %>% 
  filter(Games == "2016 Summer") %>%
  group_by(region) %>%
  summarize(Rio = length(unique(ID)))

# Create data for mapping
world <- map_data("world")
worldmap <- tibble(region=unique(world$region))
worlddat <- worldmap %>% 
  left_join(Stockholm, by="region") %>%
  left_join(Berlin, by="region") %>%
  left_join(Tokyo, by="region") %>%
  left_join(Montreal, by="region") %>%
  left_join(Moscow, by="region") %>%
  left_join(rio, by="region")
worlddat$Berlin[is.na(worldmap$Berlin)] <- 0
worlddat$Montreal[is.na(worldmap$Montreal)] <- 0
worlddat$Montreal[is.na(worldmap$Moscow)] <- 0
worlddat$Rio[is.na(worldmap$Rio)] <- 0
worlddat$Stockholm[is.na(worldmap$Stockholm)] <- 0
worlddat$Tokyo[is.na(worldmap$Tokyo)] <- 0
world <- left_join(world, worlddat,by = "region")

#1912
ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Stockholm)) +
  labs(title = "Stockholm 1912",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_line(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "cyan"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="red")
```

*****
### Before the Second World War, the number of athletes from the United States increased \n while the USSR did not participate. 
```{r}
ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Berlin)) +
  labs(title = "Berlin 1936",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_line(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "cyan"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="red")
```

******
### In 1964, Tokyo became the first country from Asia to hold the Summer Olympic Games.
```{r}
ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Tokyo)) +
  labs(title = "Tokyo 1964",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_line(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "cyan"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="red")

```

*******
### In 1976, Canada held it's first Summer Olympic Games in Montreal.
```{r}
# Montreal 1976
ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Montreal)) +
  labs(title = "Montreal 1976",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_line(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "cyan"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient2(low = "white", high = "red")
```

********
### In the year of 1980, multiple countries boycotted the Moscow Olympic Games \n due to its invasion of Afghanistan for crude oil.
```{r}
# Moscow 1980
ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Moscow)) +
  labs(title = "Moscow 1980",
       x = NULL, y = NULL) +
  theme(axis.ticks = element_line(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "cyan"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient2(low = "white", high = "red")
```

****
### Fast forward to the year of 2016, the number of participating countries reached its peak due to globalization and greater awareness for diversity and inclusion. 
```{r}
#Rio 2016
ggplot(world, aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = Rio)) +
  labs(title = "Rio 2016",
       x = NULL, y=NULL) +
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.background = element_rect(fill = "cyan"),
        plot.title = element_text(hjust = 0.5)) +
  guides(fill=guide_colourbar(title="Athletes")) +
  scale_fill_gradient(low="white",high="red")
```

## Gender Equality
### group_by()/summarize()

#### Males still dominates the Olympic Games...
```{r }
#glimpse(athletes)
df <- athletes %>%
  group_by(Season, Sex) %>%
  summarise(Count = n()) %>%
  mutate(Percentage = round(Count*100 / sum(Count))) 
  
df %>%   
ggplot(aes(x=Season, y=Percentage, fill = Sex)) + geom_bar(stat='identity',position=position_dodge()) +
        ggtitle("Proportions of Male and Female") +
        geom_label(label=c("73%", "27%", "69%", "31%"), position = position_dodge(0.9)) +
        theme_minimal() + theme(plot.title = element_text(hjust=0.5))
```

******
#### ...while there are upward trends in female participation...

```{r}
attach(athletes)

#gender trend
gender.s <- athletes %>% 
  filter(Season=="Summer") %>% 
  group_by(Year, Sex) %>% 
  summarise(
    athlete.cnt = length(unique(Name))
  )
gender.w <- athletes %>% 
  filter(Season=="Winter") %>% 
  group_by(Year, Sex) %>% 
  summarise(
    athlete.cnt = length(unique(Name))
  )

gender.s.plot <- ggplot(gender.s, aes(x = Year, y = athlete.cnt, color = Sex)) +
  geom_point(size=2) + geom_line() +
  #scale_color_manual(values = c("navy", "sandybrown")) +
  xlim(1896,2016) + ylim(0,7000) + 
  labs(title = "Number of Male and Female Atheltes (Summer)") + 
  theme(plot.title = element_text(hjust = 0.5))

gender.w.plot <- ggplot(gender.w, aes(x = Year, y = athlete.cnt, color = Sex)) +
  geom_point(size=2) + geom_line() +
  #scale_color_manual(values = c("navy", "sandybrown")) +
  xlim(1896,2016) + ylim(0, 7000) +
  labs(title = "Number of Male and Female Atheltes over Time (Winter)") + 
  theme(plot.title = element_text(hjust = 0.5))

grid.arrange(gender.s.plot, gender.w.plot)

#trends of number of sports for each gender
# sports.s.gen <- athletes %>% 
#   filter(Season=="Summer") %>% 
#   group_by(Year, Sex) %>% 
#   summarise(
#     sport.cnt = length(unique(Sport))
#     )
# 
# sports.w.gen <- athletes %>% 
#   filter(Season=="Winter") %>% 
#   group_by(Year, Sex) %>% 
#   summarise(
#     sport.cnt = length(unique(Sport))
#     )
# 
# sport.s.plot <- ggplot(sports.s.gen, aes(x = Year, y = sport.cnt, color = Sex)) + 
#   geom_point(size=2) +
#   #scale_color_manual(values = c("navy" ,"sandybrown")) +
#   labs(title = "Number of Sports for Men and Women (Summer)") +
#   ylab("Number of Athletes") + geom_line() +
#   xlab("") + ylim(0,35) +
#   theme(plot.title = element_text(hjust = 0.5))
# 
# sport.w.plot <- ggplot(sports.w.gen, aes(x = Year, y = sport.cnt, color = Sex)) + 
#   geom_point(size=2) +
#   #scale_color_manual(values = c("navy" ,"sandybrown")) +
#   labs(title = "Number of Sports for Men and Women (Winter)") +
#   ylab("Number of Athletes") + geom_line() + 
#   xlab("Year") + xlim(1896,2016) + ylim(0,35) +
#   theme(plot.title = element_text(hjust = 0.5))
# 
# 
# grid.arrange(sport.s.plot, sport.w.plot)
```

*****
#### ...and the male-to-female ratio is converging to 1
```{r}
#ratios start here
groupMale <-  athletes %>%
              filter(Sex == "M") %>%
              group_by(Year, Season) %>%
              summarise(Number_Of_Men = n())

groupFemale <- athletes %>%
              filter(Sex == "F") %>%
              group_by(Year, Season) %>%
              summarise(Number_Of_Women = n())

group <- groupMale %>%
          left_join(groupFemale) %>%
          mutate(Sex_Ratio = Number_Of_Men/Number_Of_Women)
group$Sex_Ratio[is.na(group$Sex_Ratio)] <- 175


p1 <- group %>%
    ggplot(aes(x = Year, y= Sex_Ratio, group = Season)) +
    geom_line(aes(color = Season)) +
    geom_point(aes(color = Season)) +
    labs(x = "Year", y = "Sex Ratio", title = "Male-to-Female Ratio over the Years") +
    theme_minimal() + theme(plot.title = element_text(hjust=0.5))

p2 <- group %>%
    filter(Year>1927) %>%
    ggplot(aes(x = Year, y= Sex_Ratio, group = Season)) +
    geom_line(aes(color = Season)) +
    geom_point(aes(color = Season)) +
    labs(x = "Year", y = "Sex Ratio", title = "Male-to-Female Ratio after 1927") +
    theme_minimal() + theme(plot.title = element_text(hjust=0.5))

cowplot::plot_grid(p1,p2, ncol = 1, 
          align = 'h', axis = 'l')

```

*******
## How do BMI distribution differ between Basketball Players and Weightlifting Athletes
### Basketball players tend to be taller than average people \n while weightlifting athletes needs to be shorter to have a lower center of mass

#### filter() & mutate() 
```{r}
BMI.comb <- athletes %>%
  filter(Sport == "Basketball" | Sport == "Weightlifting" & Sex=="M") %>% 
  filter(!is.na(Weight) & !is.na(Height)) %>%
  mutate(BMI = Weight/((Height/100)^2))

mean.bmi <- mean(BMI.comb$BMI)
ggplot(BMI.comb, aes(x = BMI, fill=Sport)) + geom_histogram(bins = 30) + 
  annotate("text", x = mean.bmi, y = 50, 
           label = "Mean=25.23", size=4) +
  geom_segment(mapping = aes(x=mean.bmi-0.1, xend=mean.bmi+0.1, y=0, yend=0), size = 4) +
  xlim(10,50) + xlab("BMI") + ylab("Frequency")+
  labs(title = "BMI of Basketball Players vs Weightlifting Players") +
  theme(plot.title = element_text(hjust = 0.5))


detach(athletes)
```

******
## Who won the most number of medals?
```{r}
#merge the csv file noc_region with an other file 
athletesRegion <- athletes%>%left_join(regions, by =c("NOC"="region"))
#cat("The total number of National Olympics Committees that have paricipated in the olympics are", length(unique(athletesRegion$region)))

athletesRegion %>%
  filter(Medal != "<NA>") %>%
  group_by(NOC) %>%
  summarise(Medal_Tally = length(Medal))%>%
  arrange(desc(Medal_Tally)) %>%
  ungroup() %>%
  mutate(NOC = reorder(NOC,Medal_Tally)) %>%
  top_n(10) %>%
  ggplot(aes(x = NOC,y = Medal_Tally)) +
    geom_bar(stat='identity',colour="white", fill = "tomato") +
    geom_text(aes(x = NOC, y = .1, label = paste0("(",round(Medal_Tally,2),")",sep="")),
              hjust=0, vjust=.5, size = 4, colour = 'black',
              fontface = 'bold') +
    theme(plot.title = element_text(size=10),
          axis.title = element_text(size=10),
          axis.text = element_text(size=10)) +
    labs(x = 'Country', 
         y = 'Number of Medals'
         ) +
    coord_flip() + 
    theme_bw()
```

*****
### Specifically, for the United States...
```{r}
Gold <-  athletesRegion %>%
                filter(Medal == "Gold")%>%
                group_by(Year, Season, NOC) %>%
                summarise(Gold = n())

Silver <-  athletesRegion %>%
                filter(Medal == "Silver")%>%
                group_by(Year, Season, NOC) %>%
                summarise(Silver = n())

Bronze <-  athletesRegion %>%
                filter(Medal == "Bronze")%>%
                group_by(Year, Season, NOC) %>%
                summarise(Bronze = n())

Total <-  athletesRegion %>%
                filter(Medal != "<NA>")%>%
                group_by(Year, Season, NOC) %>%
                summarise(Total = n())

Total <- Total %>%
          left_join(Gold) 

Total <- Total %>%
          left_join(Silver)

Total <- Total %>%
          left_join(Bronze)
Total$Gold[is.na(Total$Gold)] <- 0
Total$Silver[is.na(Total$Silver)] <- 0
Total$Bronze[is.na(Total$Bronze)] <- 0
Total$Total[is.na(Total$Total)] <- 0

count2 <- athletes %>%
  group_by(Year) %>%
  filter(NOC == "USA") %>%
  summarise(NumberOfAthltes = n())

NumberofMedalAthelUSA <- athletes %>%
                filter(Medal != "<NA>")%>%
                filter(NOC == "USA") %>%
                group_by(Year) %>%
                summarise(NumberOfMedals = n())
#Aggregate the data frame count and Gold_winner together, get the season region Year three variables.
TotaldataMedalUSA <- count2 %>% left_join(NumberofMedalAthelUSA, by = c("Year"))

TotaldataMedalUSA$NumberOfMedals[is.na(NumberofMedalAthelUSA$NumberOfMedals)] <- 0


count3 <- athletes %>%
  group_by(Year) %>%
  filter(NOC == "CHN") %>%
  summarise(NumberOfAthltes = n())

NumberofMedalAthelCHN <- athletes %>%
                filter(Medal != "<NA>")%>%
                filter(NOC == "CHN") %>%
                group_by(Year) %>%
                summarise(NumberOfMedals = n())
#Aggregate the data frame count and Gold_winner together, get the season region Year three variables.
TotaldataMedalCHN <- count3 %>% left_join(NumberofMedalAthelCHN, by = c("Year"))

TotaldataMedalCHN$NumberOfMedals[is.na(NumberofMedalAthelCHN$NumberOfMedals)] <- 0


MedalUSA<-TotaldataMedalUSA %>% 
        ggplot(aes(x=NumberOfAthltes, y=NumberOfMedals,color = NumberOfAthltes)) +
        geom_point(color="blue")  + geom_smooth(method = "lm", se=TRUE, color="black", aes(group=1)) +
        theme_minimal() +
        labs(x = "Number of Athletes in Team USA", y = "Number of Medals")


grid.arrange(MedalUSA, ncol=1)
```

******
## USA Outperforming the rest of the world
```{r}
TotalSu <- Total %>%
          filter(NOC %in% c("USA","RUS","GER","CAN","CHN")) %>%
          filter(Season == "Summer")

plotmedalSummer <- TotalSu %>%
  ggplot(aes(x = Year, y = Total, group = NOC)) +
  geom_line(aes(color = NOC)) +
  geom_point(aes(color = NOC)) +
  annotate("text",x=c(1916,1942),y=c(550,550),
           label=c("WWI","WWII"), size=4, color="orange") +
  geom_segment(mapping=aes(x=1914,y=500,xend=1918,yend=500),color=631, size=1) +
  geom_segment(mapping=aes(x=1939,y=500,xend=1945,yend=500),color=631, size=1) +
  annotate("text", x=c(1980,2016),
           y=c(450,450),
           label=c("Moscow 1980","Rio 2016"),
           size=3) +
  theme_minimal()+
  ggtitle("Total Number of Medals for Five Different Countries (Summer)") + 
  ylab("Number of Medals") + 
  theme(plot.title = element_text(hjust = 0.5))

TotalWin <- Total %>%
            filter(NOC %in% c("USA","RUS","GER","CAN","CHN")) %>%
            filter(Season == "Winter")

plotmedalWinter <-TotalWin %>%
  ggplot(aes(x = Year, y = Total, group = NOC)) +
  geom_line(aes(color = NOC)) +
  geom_point(aes(color = NOC)) +
  annotate("text",x=c(1942),y=c(100),
           label=c("WWII"), size=4, color="orange") +
  geom_segment(mapping=aes(x=1939,y=80,xend=1945,yend=80),color=631, size=1) +
  annotate("text", x=c(2010),
           y=c(120),
           label=c("Vancouver 2010"),
           size=3) +
  annotate("text", x=c(1976),
           y=c(120),
           label=c("Montreal 1976"),
           size=3) +
  theme_minimal()+  ylab("Number of Medals") + 
  ggtitle("Total Number of Medals for Five Different Countries (Winter)") + theme(plot.title = element_text(hjust = 0.5))

grid.arrange(plotmedalSummer, plotmedalWinter, ncol=1)
#Team Canada reaches the best result of them in Vancouver, 2010.
```

***
## Create an interactive chart using ggplotly()
```{r}
sport <- athletes%>%filter(!is.na(Medal),Season=='Summer',Year==2008)%>%left_join(regions,by=c("NOC"="NOC"))
sport$notes<-NULL
sport <- sport%>%group_by(Sport,region)%>%summarize(total=n())

slist =c('Athletics','Badminton','Baseball','Basketball','Boxing','Football','Gymnastics','Hockey','Judo',' Shooting','Swimming ','Table Tennis','Tennis','Weightlifting','Volleyball')

sport <- filter(sport,Sport%in%slist,total>=1)
sport$region <- as.factor(sport$region)

p <-ggplot(sport,aes(Sport,total,color=region,fill=region)) +
  geom_bar(position = "stack",  width =.75,stat="identity") +
  scale_x_discrete() +
  xlab("Sports")+ylab("Medals")+
  theme(legend.position = "none",
  axis.text = element_text(size = 6,face="bold"),
  plot.title = element_text(size=16,face = "bold")) + 
  ggtitle("Major sports  in 2008 games") + theme(plot.title = element_text(hjust = 0.5)) 

ggplotly(p)

```

****
## Does Home Advantage Exist?
```{r}
#home advantage
#Number of USA gold medals over the time in Summer Season
attach(athletes)
plot <- athletes %>% group_by(Year, Team, Medal) %>% 
  filter(Season=='Summer', !is.na(Medal), Medal=="Gold", !grepl('-',Team), Team=='United States') %>%summarize(Count=n()) %>% arrange(Year) %>% group_by(Year) %>% top_n(10,Count)
ggplot(plot, aes(x=Year, y=Count, group=Medal)) +
geom_line(aes(colour=Team)) +
geom_point(aes(colour=Team))+
scale_x_continuous(breaks=plot$Year)+
annotate("text", x=c(1904,1932,1984,1996),
           y=c(75,75,175,165),
           label=c("st.Louis 1904","Los Angeles 1932","Los Angeles 1984","Atlanta 1996"),
           size=3)+
  theme(legend.position="none", legend.text=element_text(size=0),axis.text.x=element_text(size=8, angle=90,vjust=0,hjust=1))+
  labs(title="Number of Golds won by USA (Summer)", x="Years", y="Num. of Medals") + 
  theme(plot.title = element_text(hjust = 0.5)) + ylab("Number of Gold Medals")
```

***
## Does Home Advantage Exist?
```{r}
attach(athletes)
plot <- athletes %>% group_by(Year, Team, Medal) %>% 
  filter(Season=='Winter', !is.na(Medal), Medal=="Gold", !grepl('-',Team), Team=='United States') %>%summarize(Count=n()) %>% arrange(Year) %>% group_by(Year) %>% top_n(10,Count)
ggplot(plot, aes(x=Year, y=Count, group=Medal)) +
geom_line(aes(colour=Team)) +
geom_point(aes(colour=Team))+
scale_x_continuous(breaks=plot$Year)+
annotate("text", x=c(1932,1960,1980,2002),
           y=c(5,20,25,10),
           label=c("Lake Placid 1932","Squaw Valley 1960","Lake Placid 1980","Salt Lake City 2002"),
           size=3)+
theme(legend.position="none", legend.text=element_text(size=0),axis.text.x=element_text(size=8, angle=90,vjust=0,hjust=0.5))+
labs(title="Number of USA gold medals over the time in Winter Season", x="Years", y="Num. of Medals")

```

***
## Does Home Advantage Exist?
```{r}
attach(athletes)
plot <- athletes %>% group_by(Year, Team, Medal) %>% 
  filter(Season=='Summer', !is.na(Medal), Medal=="Gold", !grepl('-',Team), Team=='Great Britain') %>%summarize(Count=n()) %>% arrange(Year) %>% group_by(Year) %>% top_n(10,Count)
ggplot(plot, aes(x=Year, y=Count, group=Medal)) +
geom_line(aes(colour=Team)) +
geom_point(aes(colour=Team))+
scale_x_continuous(breaks=plot$Year)+
annotate("text", x=c(1908,1948,2012),
           y=c(75,10,50),
           label=c("London 1908","London 1948","London 2012"),
           size=3)+
  theme(legend.position="none", legend.text=element_text(size=0),axis.text.x=element_text(size=8, angle=90,vjust=0,hjust=1),
        plot.title = element_text(hjust=0.5))+
  labs(title="Number of Golds won by Great Britain (Summer)", x="Years", y="Number of Gold Medals")
  
```

***
## Does Home Advantage Exist?
```{r}
counts <- athletes %>% filter(Team== "United States",Season=="Summer") %>%
  group_by(Year, Season) %>%
  summarize(
    Athletes = length(unique(ID)),
    Nations = length(unique(NOC)),
    Events = length(unique(Event))
  )

p1 <- ggplot(counts, aes(x=Year, y=Athletes, group=Season)) +
  geom_point(size=2) +
  geom_line() +
  scale_color_manual(values=c("darkorange","darkblue")) +
  xlab("")+
  annotate("text", x=c(1904,1932,1984,1996),
           y=c(400,400,500,600),
           label=c("st.Louis 1904","Los Angeles 1932","Los Angeles 1984","Atlanta 1996"),
           size=3)+
  labs(title="USA- Participation over the time in Summer Season") + theme(plot.title = element_text(hjust=0.5))
  
  
grid.arrange(p1, ncol=1)
```

- Higher degree of participation
- travel fatigue 

***** 
## Conclusion 

- Globalization and greater diversity welcomes more countries and more women to participate in the Olympic Games. 
- Want to win the most number of medals? Wait till your home country holds the Olympic Games! 
